Nope

### 2010-12-14 AffineLieAlgebras/MQFT2010/article.tex
Merge with V.D. version

\documentclass[12pt]{article}
%\usepackage{ucs}
\usepackage{amsmath,amssymb,amsthm}
%\usepackage{pb-diagram}
\usepackage{multicol}
\usepackage{cmap}
\usepackage{color}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{hyperref}

@@

To show this we use the recursive approach to branching presented in \cite{2010arXiv1007.0318L} (similar to the one used in \cite{ilyin812pbc} for maximal
embeddings). We consider the subalgebra $\frak{a}$ together with its
counterpart $\frak{a}_{\bot }$ ''orthogonal'' to $\frak{a}$ with respect to
the Killing form and also $\widetilde{\frak{a}_{\perp }}:=\frak{a}_{\perp
}\oplus \frak{h}_{\perp }$ where $\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus 
\frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$. For any reductive
algebra $\frak{a}$ the subalgebra $\frak{a}_{\bot }\hookrightarrow \frak{g}$
is regular and reductive. For a highest weight integrable module $L^{\left(
\mu \right) }$ and orthogonal pair of subalgebras $\left( \frak{a},\frak{a}%
_{\bot }\right) $ we consider the singular element $\Psi ^{\left( \mu
\right) }$ (the numerator in the Weyl character formula $ch\left( L^{\mu
}\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$, see
for example \cite{humphreys1997introduction}) the Weyl denominator $R=\Psi _{%
\frak{a}_{\bot }}^{\left( 0\right) }$ and the projection $\Psi _{\left( 
\frak{a},\frak{a}_{\bot }\right) }^{\left( \mu \right) }=\pi _{\frak{a}}%
\frac{\Psi _{\frak{g}}^{\left( \mu \right) }}{\Psi _{\frak{a}_{\bot
}}^{\left( 0\right) }}$. The element $\Psi _{\frak{g}}^{\left( \mu \right) }$
can be decomposed with respect to the set of Weyl numerators $\Psi _{\frak{a}%
_{\bot }}^{\left( \mu \right) }$ of $\frak{a}_{\bot }$. This decomposition
provides the possibility to construct the set of highest weight modules $L_{%
\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}}$. When
the injection \ $\frak{a}_{\bot }\hookrightarrow \frak{g}$ \ satisfies the
''standard parabolic'' conditions these modules give rise to the parabolic
Verma modules $M_{\left( \widetilde{\frak{a}_{\perp }}\hookrightarrow \frak{g%
}\right) }^{\mu _{\widetilde{\frak{a}_{\perp }}}}$ so that the initial
character $ch\left( L^{\mu }\right) $ is finally decomposed into the
alternating sum of such. On the other hand when the parabolic conditions are
violated the construction survives and exhibites a decomposition with
respect to a set of Verma modules $M_{\left( \widetilde{\frak{b}_{\perp }},%
\frak{g}\right) }^{\mu _{\widetilde{\frak{a}_{\perp }}}}$. In such a
situation the algebra $\widetilde{\frak{b}_{\perp }}$ is not a subalgebra in 
$\frak{g}$ but a contraction of $\widetilde{\frak{a}_{\perp }}$.

@@

@@

$\stackrel{\circ }{\Delta}$ , $\left( \stackrel{\circ }{\Delta _{\frak{a}}}%
\right)$ --- the finite root system of the subalgebra $\stackrel{\circ }{%
\frak{g}}$ (resp. $\stackrel{\circ }{\frak{a}}$);

$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
the weight diagram of $L^{\mu }$ $\left( \mathrm{{resp. }L_{\frak{a}}^{\nu }}%
\right) $ ;

@@

$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
i $-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mathrm{{resp. }%
\frak{a}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}%
}\right) $;

$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
}\right) $--- the basic coroot for $\frak{g}$ $\left( \mathrm{{resp. }\frak{a%
}}\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;

$\stackrel{\circ }{\xi }$ , $\stackrel{\circ }{\xi _{\left( \frak{a}\right) }%
}$ --- the finite (classical) part of the weight $\xi \in P$ , $\left( 
\mathrm{{resp. }\xi _{\left( \frak{a}\right) }\in P_{\frak{a}}}\right) $;

@@

Let us introduce the ''orthogonal partner'' $\frak{a}_{\bot }$ for a
reductive subalgebra $\frak{a}$ in $\frak{g}$.

Consider the root subspace $\frak{h}_{\perp \frak{a}}^{\ast }$ orthogonal to 
$\frak{a}$, 
\[
\frak{h}_{\perp \frak{a}}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
h\in \frak{h}_{\frak{a}};\eta \left( h\right) =0\right\} , 
\]
and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
to $\frak{a}$, 
\begin{eqnarray*}
\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} , \\
\Delta _{\frak{a}_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
}^{+}|\forall h\in \frak{h}_{\frak{a}};\beta ^{+}\left( h\right) =0\right\} .
\end{eqnarray*}
Let $W_{\frak{a}_{\perp }}$ be the subgroup of $W$ generated by the
reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\frak{a}_{\perp
}}^{+}$ . The subsystem $\Delta _{\frak{a}_{\perp }}$ determines the
subalgebra $\frak{a}_{\perp }$ with the Cartan subalgebra $\frak{h}_{\frak{a}%
_{\perp }}$. Let 
\[
\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \frak{a}}^{\ast
}|\forall h\in \frak{h}_{\frak{a}\oplus \frak{a}_{\perp }};\eta \left(
h\right) =0\right\} 
\]
so that $\frak{g}$ has the subalgebras 
\begin{eqnarray*}
\widetilde{\frak{a}_{\perp }} &:&=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
\\
\widetilde{\frak{a}} &:&=\frak{a}\oplus \frak{h}_{\perp }.
\end{eqnarray*}
Algebras $\frak{a}$ and $\frak{a}_{\perp }$ form the ''orthogonal pair'' $%
\left( \frak{a},\frak{a}_{\perp }\right) $ of subalgebras in $\frak{g}$.

For the Cartan subalgebras we have the decomposition 
\begin{equation}
\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus 
\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\frak{a}}}}\oplus \frak{h}_{%
\frak{a}_{\perp }}=\frak{\frak{h}_{\widetilde{\frak{a}_{\perp }}}}\oplus 
\frak{h}_{\frak{a}}.
\end{equation}
For the subalgebras of an orthogonal pair $\left( \frak{a},\frak{a}_{\perp
}\right) $ we consider the corresponding Weyl vectors, $\rho _{\frak{a}}$
and $\rho _{\frak{a}_{\perp }}$ , and\ form the so called ''defects'' $%
\mathcal{D}_{\frak{a}}$ and $\mathcal{D}_{\frak{a}_{\perp }}$ of the
injection: 
\begin{equation}
\mathcal{D}_{\frak{a}}:=\rho _{\frak{a}}-\pi _{\frak{a}}\rho ,
\end{equation}
\begin{equation}
\mathcal{D}_{\frak{a}_{\perp }}:=\rho _{\frak{a}_{\perp }}-\pi _{\frak{a}%
_{\perp }}\rho .
\end{equation}

For the highest weight $\mu \in P^{+}$ consider the linked weights $\left\{
\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $ and their projections to 
$h_{\widetilde{\frak{a}_{\perp }}}^{\ast }$ additionally shifted by the
defect $-\mathcal{D}_{\frak{a}_{\perp }}$: 
\[
\mu _{\widetilde{\frak{a}_{\perp }}}\left( w\right) :=\pi _{\widetilde{\frak{%
a}_{\perp }}}\left[ w(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp
}},\quad w\in W. 
\]
In the case we do consider here among the weights $\left\{ \mu _{\widetilde{%
\frak{a}_{\perp }}}\left( w\right) |w\in W\right\} $ one can always choose
those located in the fundamental chamber $\overline{C_{\widetilde{\frak{a}%
_{\perp }}}}$. Let $U$ be the set of representatives $u$ for the classes $%
W/W_{\frak{a}_{\perp }}$ such that

\begin{equation}
U:=\left\{ u\in W|\quad \mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right)
\in \overline{C_{\widetilde{\frak{a}_{\perp }}}}\right\} \quad .
\label{U-def}
\end{equation}
For such a set $U$ introduce the weights 
\[
\mu _{\frak{a}}\left( u\right) :=\pi _{\frak{a}}\left[ u(\mu +\rho )-\rho %
\right] +\mathcal{D}_{\frak{a}_{\perp }}. 
\]

@@

Consider the Weyl-Kac formula for $ch\left( L^{\mu }\right) $ in terms of
singular elements \cite{humphreys1997introduction}: 
\begin{equation}
ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left(
0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R},  \label{Weyl-Kac2}
\end{equation}
where 
\[
\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu
+\rho )-\rho }. 
\]
The same form will be used for the submodules $ch\left( L_{\frak{a}}^{\nu
}\right) $%
\[
ch\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi _{\frak{a}}^{\left( \nu
\right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
}^{\left( \nu \right) }}{R_{\frak{a}}}, 
\]
with 
\[
\Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
}}\epsilon (w)e^{w\circ (\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}. 
\]

@@

To describe the recurrent properties for branching coefficients $b_{\nu
}^{(\mu )}$ we shall use the technique first proposed in \cite{ilyin812pbc}.
One of the main tools is the set of weights $\Gamma _{\frak{a}\rightarrow 
\frak{g}}$ called the injection fan:

\begin{definition}
\label{fan-definition} For the product 
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
_{\frak{a}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\frak{a}%
}(\pi _{\frak{a}}\alpha )}=-\sum_{\gamma \in P_{\frak{a}}}s(\gamma
)e^{-\gamma }  \label{eq:6}
\end{equation}
consider the carrier $\Phi _{\frak{a}\subset \frak{g}}\subset P_{\frak{a}}$
of the function $s(\gamma )=\det \left( \gamma \right) $ : 
\begin{equation}
\Phi _{\frak{a}\subset \frak{g}}=\left\{ \gamma \in P_{\frak{a}}|s(\gamma
)\neq 0\right\}   \label{eq:37}
\end{equation}
The ordering of roots in $\stackrel{\circ }{\Delta _{\frak{a}}}$ induce the
natural ordering of the weights in $P_{\frak{a}}$. Denote by $\gamma _{0}$
the lowest vector of $\Phi _{\frak{a}\subset \frak{g}}$ . The set 
\begin{equation}
\Gamma _{\frak{a}\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in \Phi
_{\frak{a}\subset \frak{g}}\right\} \setminus \left\{ 0\right\} 
\label{fan-defined}
\end{equation}
is called the \textit{injection fan}.
\end{definition}

It must be noticed that the injection fan is the universal instrument that
depend only on the injection.

>>>>

\documentclass[12pt]{article}
%\usepackage{ucs}
\usepackage{amsmath,amssymb,amsthm}
%\usepackage{pb-diagram}
\usepackage{multicol}
\usepackage{color}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{hyperref}

@@

To show this we use the recursive approach to branching presented in \cite{2010arXiv1007.0318L} (similar to the one used in \cite{ilyin812pbc} for maximal
embeddings). We consider the subalgebra $\frak{a}$ together with its
counterpart $\frak{a}_{\bot }$ ''orthogonal'' to $\frak{a}$ with respect to
the Killing form and also $\widetilde{\frak{a}_{\perp }}:=\frak{a}_{\perp
}\oplus \frak{h}_{\perp }$ where $\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus 
\frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$. For any reductive
algebra $\frak{a}$ the subalgebra $\frak{a}_{\bot }\hookrightarrow \frak{g}$
is regular and reductive. For a highest weight integrable module $L^{\left(
\mu \right) }$ and orthogonal pair of subalgebras $\left( \frak{a},\frak{a}%
_{\bot }\right) $ we consider the singular element $\Psi ^{\left( \mu
\right) }$ (the numerator in the Weyl character formula $ch\left( L^{\mu
}\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left( 0\right) }}$, see
for example \cite{humphreys1997introduction}) the Weyl denominator $\Psi _{%
\frak{a}_{\bot }}^{\left( 0\right) }$ and the projection $\Psi _{\left(
\frak{a},\frak{a}_{\bot }\right) }^{\left( \mu \right) }=\pi _{\frak{a}}%
\frac{\Psi _{\frak{g}}^{\left( \mu \right) }}{\Psi _{\frak{a}_{\bot
}}^{\left( 0\right) }}$. The element $\Psi _{\frak{g}}^{\left( \mu \right) }$
can be decomposed with respect to the set of Weyl numerators $\Psi _{\frak{a}%
_{\bot }}^{\left( \mu \right) }$ of $\frak{a}_{\bot }$. This decomposition
provides the possibility to construct the set of highest weight modules $L_{%
\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}}$. When
the injection \ $\frak{a}_{\bot }\hookrightarrow \frak{g}$ \ satisfies the
''standard parabolic'' conditions these modules give rise to the parabolic
Verma modules $M_{\left( \widetilde{\frak{a}_{\perp }}\hookrightarrow \frak{g%
}\right) }^{\mu _{\widetilde{\frak{a}_{\perp }}}}$ so that the initial
character $ch\left( L^{\mu }\right) $ is finally decomposed into the
alternating sum of such. On the other hand when the parabolic conditions are
violated the construction survives and exhibites a decomposition with
respect to a set of Verma modules $M_{\left( \widetilde{\frak{b}_{\perp }},%
\frak{g}\right) }^{\mu _{\widetilde{\frak{a}_{\perp }}}}$. In such a
situation the algebra $\widetilde{\frak{b}_{\perp }}$ is not a subalgebra in 
$\frak{g}$ but a contraction of $\widetilde{\frak{a}_{\perp }}$.

@@

$\frak{g=n}^{-}+\frak{b}+\frak{n}^{+}$ --- the Cartan decomposition;

@@

$S\quad \left( S_{\frak{a}}\right) $ --- the system of simple roots (of $%
\frak{g}$ and $\frak{a}$ respectively);

$\stackrel{\circ }{\Delta }$ , $\left( \stackrel{\circ }{\Delta _{\frak{a}}}%
\right) $ --- the finite root system of the subalgebra $\stackrel{\circ }{%
\frak{g}}$ (resp. $\stackrel{\circ }{\frak{a}}$);

$\alpha _{i}$ , $\left( \alpha _{\left( \frak{a}\right) j}\right) $ --- the $%
i$-th (resp. $j$-th) basic root for $\frak{g}$ $\left( \mathrm{{resp.}\frak{a%
}}\right) $; $i=0,\ldots ,r$,\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;

$\alpha _{i}^{\vee }$ , $\left( \alpha _{\left( \frak{a}\right) j}^{\vee
}\right) $--- the basic coroot for $\frak{g}$ $\left( \mathrm{{resp.}\frak{a}%
}\right) $ , $i=0,\ldots ,r$ ;\ \ $\left( j=0,\ldots ,r_{\frak{a}}\right) $;

@@

$\mathcal{N}^{\mu }$ , $\left( \mathcal{N}_{\frak{a}}^{\nu }\right) $ ---
the weight diagram of $L^{\mu }$ $\left( \mathrm{{resp.}L_{\frak{a}}^{\nu }}%
\right) $ ;

$\stackrel{\circ }{\xi }$ , $\stackrel{\circ }{\xi _{\left( \frak{a}\right) }%
}$ --- the finite (classical) part of the weight $\xi \in P$ , $\left(
\mathrm{{resp.}\xi _{\left( \frak{a}\right) }\in P_{\frak{a}}}\right) $;

@@

Now we shall show how the branching procedure naturally produces the
generalized Verma modules.

Consider in $\frak{g}$ a reductive subalgebra $\frak{a}$ with the Cartan
subalgebra $\frak{h}_{\frak{a}}$. For $\frak{a}\hookrightarrow \frak{g}$
introduce the ''orthogonal partner'' $\frak{a}_{\bot }\hookrightarrow \frak{g%
}$ .

Firstly consider the root subspace $\frak{h}_{\perp \frak{a}}^{\ast }$
orthogonal to $\frak{a}$,
\[
\frak{h}_{\perp \frak{a}}^{\ast }:=\left\{ \eta \in \frak{h}^{\ast }|\forall
h\in \frak{h}_{\frak{a}};\eta \left( h\right) =0\right\} , 
\]
and the roots (correspondingly -- positive roots) of $\frak{g}$ orthogonal
to $\frak{a}$, 
\begin{eqnarray*}
\Delta _{\frak{a}_{\perp }} &:&=\left\{ \beta \in \Delta _{\frak{g}}|\forall
h\in \frak{h}_{\frak{a}};\beta \left( h\right) =0\right\} , \\
\Delta _{\frak{a}_{\perp }}^{+} &:&=\left\{ \beta ^{+}\in \Delta _{\frak{g}%
}^{+}|\forall h\in \frak{h}_{\frak{a}};\beta ^{+}\left( h\right) =0\right\} .
\end{eqnarray*}
Let $W_{\frak{a}_{\perp }}$ be the subgroup of $W$ generated by the
reflections $w_{\beta }$ with the roots $\beta \in \Delta _{\frak{a}_{\perp
}}^{+}$ . The subsystem $\Delta _{\frak{a}_{\perp }}$ determines the
subalgebra $\frak{a}_{\perp }$ with the Cartan subalgebra $\frak{h}_{\frak{a}%
_{\perp }}$. Let 
\[
\frak{h}_{\perp }^{\ast }:=\left\{ \eta \in \frak{h}_{\perp \frak{a}}^{\ast
}|\forall h\in \frak{h}_{\frak{a}\oplus \frak{a}_{\perp }};\eta \left(
h\right) =0\right\} 
\]
so that $\frak{g}$ has the subalgebras 
\begin{eqnarray*}
\widetilde{\frak{a}_{\perp }} &:&=\frak{a}_{\perp }\oplus \frak{h}_{\perp }
\\
\widetilde{\frak{a}} &:&=\frak{a}\oplus \frak{h}_{\perp }.
\end{eqnarray*}

For the Cartan subalgebras we have the decomposition 
\begin{equation}
\frak{h}=\frak{\frak{h}_{\frak{a}}}\oplus \frak{h}_{\frak{a}_{\perp }}\oplus 
\frak{h}_{\perp }=\frak{\frak{h}_{\widetilde{\frak{a}}}}\oplus \frak{h}_{%
\frak{a}_{\perp }}=\frak{\frak{h}_{\widetilde{\frak{a}_{\perp }}}}\oplus 
\frak{h}_{\frak{a}}.
\end{equation}
For the subalgebras $\frak{a}$ and $\frak{a}_{\perp }$ consider the
corresponding Weyl vectors, $\rho _{\frak{a}}$ and $\rho _{\frak{a}_{\perp }}
$ , and\ form the so called ''defects'' $\mathcal{D}_{\frak{a}}$ and $%
\mathcal{D}_{\frak{a}_{\perp }}$ of the injection:
\begin{equation}
\mathcal{D}_{\frak{a}}:=\rho _{\frak{a}}-\pi _{\frak{a}}\rho ,
\end{equation}
\begin{equation}
\mathcal{D}_{\frak{a}_{\perp }}:=\rho _{\frak{a}_{\perp }}-\pi _{\frak{a}%
_{\perp }}\rho .  \label{defect ort}
\end{equation}

For the highest weight $\mu \in P^{+}$ consider the linked weights $\left\{
\left( w(\mu +\rho )-\rho \right) |w\in W\right\} $ and their projections to 
$h_{\widetilde{\frak{a}_{\perp }}}^{\ast }$ additionally shifted by the
defect $-\mathcal{D}_{\frak{a}_{\perp }}$: 
\[
\mu _{\widetilde{\frak{a}_{\perp }}}\left( w\right) :=\pi _{\widetilde{\frak{%
a}_{\perp }}}\left[ w(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp
}},\quad w\in W. 
\]
For $\mu \in P^{+}$ among the weights $\left\{ \mu _{\widetilde{\frak{a}%
_{\perp }}}\left( w\right) |w\in W\right\} $ one can always choose those
located in the fundamental chamber $\overline{C_{\widetilde{\frak{a}_{\perp }%
}}}$. Let $U$ be the set of representatives $u$ for the classes $W/W_{\frak{a%
}_{\perp }}$ such that

\begin{equation}
U:=\left\{ u\in W|\quad \mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right)
\in \overline{C_{\widetilde{\frak{a}_{\perp }}}}\right\} \quad .
\label{U-def}
\end{equation}
Thus we can select the following subsets:
\begin{equation}
\mu _{\frak{a}}\left( u\right) :=\pi _{\frak{a}}\left[ u(\mu +\rho )-\rho %
\right] +\mathcal{D}_{\frak{a}_{\perp }},\quad u\in U,  \label{mu-a}
\end{equation}
and
\begin{equation}
\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) :=\pi _{\widetilde{\frak{%
a}_{\perp }}}\left[ u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp
}},\quad u\in U.  \label{mu-a-tilda}
\end{equation}

@@

For the modules we are interested in the Weyl-Kac formula for $ch\left( L^{\mu }\right) $ can be
written in terms of
singular elements \cite{humphreys1997introduction}
\[
\Psi ^{\left( \mu \right) }:=\sum\limits_{w\in W}\epsilon (w)e^{w\circ (\mu
+\rho )-\rho },
\]
namely,
\begin{equation}
ch\left( L^{\mu }\right) =\frac{\Psi ^{\left( \mu \right) }}{\Psi ^{\left(
0\right) }}=\frac{\Psi ^{\left( \mu \right) }}{R}.  \label{Weyl-Kac2}
\end{equation}
The same is true for the submodules $ch\left( L_{\frak{a}}^{\nu }\right) $
in (\ref{branching1})
\[
ch\left( L_{\frak{a}}^{\nu }\right) =\frac{\Psi _{\frak{a}}^{\left( \nu
\right) }}{\Psi _{\frak{a}}^{\left( 0\right) }}=\frac{\Psi _{\frak{a}%
}^{\left( \nu \right) }}{R_{\frak{a}}}, 
\]
with 
\[
\Psi _{\frak{a}}^{\left( \nu \right) }:=\sum\limits_{w\in W_{\frak{a}%
}}\epsilon (w)e^{w\circ (\nu +\rho _{_{\frak{a}}})-\rho _{_{\frak{a}}}}. 
\]

@@

\subsection{Decomposing the singular element.}

\label{subsec:decomp-sing-element}

Now we shall perform a decomposition of the singular element $\Psi ^{\left(
\mu \right) }$ in terms of singular elements of the orthogonal subalgebra
modules:

\begin{lemma}
Let $\frak{a}_{\bot }$ be the orthogonal partner of a reductive subalgebra $%
\frak{a}\hookrightarrow \frak{g}$ with $\frak{h}=\frak{\frak{h}_{\frak{a}}}%
\oplus \frak{h}_{\frak{a}_{\perp }}\oplus \frak{h}_{\perp }$, $\widetilde{%
\frak{a}_{\perp }}=\frak{a}_{\perp }\oplus \frak{h}_{\perp }$ and $%
\widetilde{\frak{a}}=\frak{a}\oplus \frak{h}_{\perp }$.

$L^{\mu }$ be the highest weight integrable module with $\mu \in P^{+}$ and

$\Psi ^{\left( \mu \right) }$\ -- the singular element of $L^{\mu }$.

Then the element $\Psi ^{\left( \mu \right) }$ can be decomposed into the
sum over $u\in U$ (see (\ref{U-def})) of singular elements $\Psi _{%
\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left(
u\right) }$ with the coefficients $\epsilon (u)e^{\mu _{\frak{a}}\left(
u\right) }$:
\begin{equation}
\Psi ^{\left( \mu \right) }=\sum_{u\in U}\;\epsilon (u)e^{\mu _{\frak{a}%
}\left( u\right) }\Psi _{\widetilde{\frak{a}_{\perp }}}^{\mu _{\widetilde{%
\frak{a}_{\perp }}}\left( u\right) }.  \label{sing decomp main}
\end{equation}
\end{lemma}

\begin{proof}
With $u\in U$ and $v\in W_{\frak{a}_{\bot }}$ perform the decomposition
\[
u(\mu +\rho )=\pi _{\left( \frak{a}\right) }u(\mu +\rho )+\pi _{\left(
\widetilde{\frak{a}_{\perp }}\right) }u(\mu +\rho )
\]
for the singular weight $vu(\mu +\rho )-\rho $:
\begin{equation}
\begin{array}{lcl}
vu(\mu +\rho )-\rho  & = & \pi _{\left( \frak{a}\right) }\left( u(\mu +\rho
)\right) -\rho +\rho _{\frak{a}_{\perp }}+\pi _{\left( \frak{h}_{\bot
}\right) }\rho  \\
&  & +\ v\left( \pi _{\left( \widetilde{\frak{a}_{\perp }}\right) }u(\mu
+\rho )-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\rho _{%
\frak{a}_{\perp }}-\pi _{\left( \frak{h}_{\bot }\right) }\rho .
\end{array}
\label{sing-decomp-1}
\end{equation}
Use the defect $\mathcal{D}_{\frak{a}_{\bot }}$ (\ref{defect-perp}) to
simplify the first summand in (\ref{sing-decomp-1}):
\[
\begin{array}{r}
\pi _{\left( \frak{a}\right) }\left( u(\mu +\rho )\right) -\rho +\rho _{%
\frak{a}_{\perp }}+\pi _{\left( \frak{h}_{\bot }\right) }\rho = \\
\pi _{\left( \frak{a}\right) }\left( u(\mu +\rho )\right) -\pi _{\frak{a}%
}\rho -\pi _{\frak{a}_{\bot }}\rho +\rho _{\frak{a}_{\bot }}= \\
=\pi _{\left( \frak{a}\right) }\left( u(\mu +\rho )-\rho \right) +\mathcal{D}%
_{\frak{a}_{\bot }},
\end{array}
\]
and the second one:
\[
\begin{array}{c}
v\left( \pi _{\left( \widetilde{\frak{a}_{\perp }}\right) }u(\mu +\rho
)-\rho _{\frak{a}_{\perp }}+\rho _{\frak{a}_{\perp }}\right) -\rho _{\frak{a}%
_{\perp }}-\pi _{\left( \frak{h}_{\bot }\right) }\rho = \\
v\left( \pi _{\left( \widetilde{\frak{a}_{\bot }}\right) }u(\mu +\rho )-%
\mathcal{D}_{\frak{a}_{\bot }}-\pi _{\left( \frak{a}_{\bot }\right) }\rho
-\pi _{\left( \frak{h}_{\bot }\right) }\rho +\rho _{\frak{a}_{\bot }}\right)
-\rho _{\frak{a}_{\bot }}= \\
=v\left( \pi _{\left( \widetilde{\frak{a}_{\bot }}\right) }\left[ u(\mu
+\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\bot }}+\rho _{\frak{a}_{\bot
}}\right) -\rho _{\frak{a}_{\bot }}.
\end{array}
\]
These expressions provide the desired factorization of the singular element $%
\Psi ^{\mu }$ in terms of singular elements $\Psi _{\widetilde{\frak{a}%
_{\perp }}}^{\eta }$ of the $\widetilde{\frak{a}_{\perp }}$-modules $L_{%
\widetilde{\frak{a}_{\perp }}}^{\eta }$:
\begin{equation}
\begin{array}{l}
\Psi ^{\mu }=\sum_{u\in U}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
(v)\epsilon (u)e^{vu(\mu +\rho )-\rho }= \\
=\sum_{u\in U}\epsilon (u)e^{\pi _{\frak{a}}\left[ u(\mu +\rho )-\rho \right]
+\mathcal{D}_{\frak{a}_{\perp }}}\sum_{v\in W_{\frak{a}_{\perp }}}\epsilon
(v)e^{v\left( \pi _{\left( \widetilde{\frak{a}_{\perp }}\right) }\left[
u(\mu +\rho )-\rho \right] -\mathcal{D}_{\frak{a}_{\perp }}+\rho _{\frak{a}%
_{\perp }}\right) -\rho _{\frak{a}_{\perp }}}= \\
=\sum_{u\in U}\;\epsilon (u)\Psi _{\widetilde{\frak{a}_{\perp }}}^{\pi
_{\left( \widetilde{\frak{a}_{\perp }}\right) }\left[ u(\mu +\rho )-\rho
\right] -\mathcal{D}_{\frak{a}_{\perp }}}e^{\pi _{\left( \frak{a}\right) }%
\left[ u(\mu +\rho )-\rho \right] +\mathcal{D}_{\frak{a}_{\perp }}}.
\end{array}
\label{singular main}
\end{equation}
\end{proof}

\bigskip

\begin{remark}
This relation can be considered as a generalized form of the Weyl formula
for the singular element $\Psi _{\frak{g}}^{\mu }$: the vectors $\mu _{\frak{%
a}}\left( u\right) $ play the role of singular weights while the alternating
factors $\epsilon (u)$ are extended to $\epsilon (u)\Psi _{\widetilde{\frak{a%
}_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) }$. In
fact when $\frak{a=g}$ both $\frak{a}_{\perp }$and $\frak{h}_{\perp }$are
zeros, $U=W$, and\ the original Weyl formula is reobtained via the
trivilization of the singular elements: $\epsilon (u)\Psi _{\widetilde{\frak{%
a}_{\perp }}}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right)
}=\epsilon (u)$. In the opposite limit when $\frak{a=0}$, $\Delta _{\frak{a}%
_{\perp }}=\Delta _{\frak{g}}$, $\frak{h}_{\perp }^{\ast }=0$, $\widetilde{%
\frak{a}_{\perp }}=\frak{g}$, $\mathcal{D}_{\frak{a}_{\perp }}=0$, $U=W/W_{%
\frak{a}_{\perp }}=e$ and $\Psi ^{\mu }$ is again reobtained, now via the
trivilization of the set of vectors: $\mu _{\frak{a}}\left( e\right) =0$.
\end{remark}

\begin{remark}
In [our preprint] the decomposition analogous to (\ref{singular main}) was
used to construct the recurrent relations for branching coefficients $k_{\xi
}^{\left( \mu \right) }$ corresponding to the injection $\frak{a}%
\hookrightarrow \frak{g}$:
\[
\begin{array}{c}
k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
\sum_{u\in U}\epsilon (u)\;\dim \left( L_{\widetilde{\frak{a}_{\perp }}%
}^{\mu _{\widetilde{\frak{a}_{\perp }}}\left( u\right) }\right) \delta _{\xi
-\gamma _{0},\pi _{\frak{a}}(u(\mu +\rho )-\rho )}+\right.  \\
\left. +\sum_{\gamma \in \Gamma _{\frak{a}\rightarrow \frak{g}}}s\left(
\gamma +\gamma _{0}\right) k_{\xi +\gamma }^{\left( \mu \right) }\right) .
\end{array}
\]
The recursion is goverened by the set $\Gamma _{\frak{a}\rightarrow \frak{g}}
$ called the injection fan. The latter is defined the carrier set $\left\{
\xi \right\} _{\frak{a}\rightarrow \frak{g}}$ for the coefficient function $%
s(\xi )$
\[
\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}:=\left\{ \xi \in P_{%
\frak{a}}|s(\xi )\neq 0\right\}
\]
appearing in the expansion
\begin{equation}
\prod_{\alpha \in \Delta ^{+}\setminus \Delta _{\bot }^{+}}\left( 1-e^{-\pi
_{\frak{a}}\alpha }\right) ^{\mathrm{mult}(\alpha )-\mathrm{mult}_{\frak{a}%
}(\pi _{\frak{a}}\alpha )}=-\sum_{\gamma \in P_{\frak{a}}}s(\gamma
)e^{-\gamma };\quad
\end{equation}
The weights in $\left\{ \xi \right\} _{\frak{a}\rightarrow \frak{g}}$ are to
be shifted by $\gamma _{0}$ -- the lowest vector in $\left\{ \xi \right\} $
-- and the zero element is to be eliminated:
\begin{equation}
\Gamma _{\frak{a}\rightarrow \frak{g}}=\left\{ \xi -\gamma _{0}|\xi \in
\left\{ \xi \right\} \right\} \setminus \left\{ 0\right\} .
\end{equation}
\end{remark}

\subsection{Weyl like formulas.}
